Model LF

### 2022-12-08 Power point test.Rmd
Commit

@@

>>>>

```{r}
wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_00 = S_model$simulation$wage_ds
u_ds_00 = S_model$simulation$u_ds
```

@@

plot(wage_gap1_bs2, col= "black", xlab= "Year", ylab= "Wage gap (ratio)", main= "Wage Gap in baseline");
lines(wage_gap1_00, col= "red");
grid()

plot(wage_ds_bs2, col= "black", xlab= "Year", ylab= "Wages (level)", main= "Wages in baseline");
lines(wage_ds_00, col= "red");
grid()
